Empty Homes V1

### 2017-03-28 EmptyHomesV1.Rmd
Removed the initial borough plotting. Added in the rural boroughs. Added in code for creating a single borough plot using the XXXDAT format

@@

@@

```{r}
setwd("/home/jonno/Dropbox/SSE/Empty Homes/Regions-Complete/Region London")
list.files()

test <- read.xlsx("SuttonExemptionsLSOA.xlsx")
ken1 <- read.xlsx("Copy of Kensington and ChelseaCTBandsLSOA.xlsx" )
ken2 <- read.xlsx("NewhamExemptionsLSOA.XLSX")[,1:4]
```

```{r}
setwd(ShapeFiles)

wards.shp <- readShapeSpatial("London_Ward.shp")
coords <- coordinates(wards.shp)
WardsAdj <- poly2nb(wards.shp, queen= FALSE)
plot(wards.shp, border="grey")
plot(WardsAdj, coords, add=TRUE, col="red")

test <- (nb2mat(WardsAdj)>0)*1

g=graph.data.frame(WardsAdj)
get.adjacency(WardsAdj,sparse=FALSE)

@@

if(file.exists(file.path(DataFolder,"shapeframe.rds"))){
 PstCdLSOA.raw <- readRDS(file.path(DataFolder,"shapeframe.rds"))
} else{
    setwd(LSOAshapedata)

@@

other borough
```{r}
setwd("/home/jonno/Dropbox/SSE/Empty Homes/Regions-Complete/Region London")
list.files()

test <- read_excel("Copy of Haringey_Exemptions_Discounts_LSOA.xlsx")[,c(1,4:6)] %>% setNames(make.names(names(.)))

test2 <- test %>% group_by(LSOA_CODE, Exemption.type) %>% summarise(Counts = n())

test2b <- test %>% 
  mutate(type2 = ifelse(grepl("Empty", Exemption.type), "Empty", Exemption.type)) %>%
  group_by(type2) %>% summarise(Counts = n())

test2b <- test %>% 
  mutate(type2 = ifelse(grepl("Empty", Exemption.type), "Empty", Exemption.type)) %>%
  group_by(type2, LSOA_CODE) %>% "Hammersmith.xls"  
  summarise(Counts = n()) %>% 
  spread(., type2, Counts, fill = 0)

test3 <- test2b %>% left_join(., select(EW2, ECODE:Pop), by = c("LSOA_CODE" = "ECODE")) %>%
   mutate(EmptPerc = Empty/Homes)

Load lambeth data
```{r}
setwd("/home/jonno/Dropbox/SSE/Empty Homes/Regions-Complete/Region London")
list.files()

test <- read_excel("LambethExemptionsLSOA.xlsx")[,1:4] %>% setNames(make.names(names(.)))

test2b <- test %>% 
  mutate(type2 = ifelse(grepl("Empty", Exemption.type), "Empty", Exemption.type)) %>%
  group_by(type2, LSOA_CODE) %>% 
  summarise(Counts = n()) %>% 
  spread(., type2, Counts, fill = 0)

test3 <- test2b %>% left_join(., select(EW2, ECODE:Pop), by = c("LSOA_CODE" = "ECODE")) %>%
   mutate(EmptPerc = Empty/Homes)

Filter to lambeth and plot
```{r}
AG2 <- AG %>% filter(LAD11NM == "Lambeth") %>% 
  left_join(., test2b, by = c("lsoa11cd" = "LSOA_CODE")) %>% mutate(EmptPerc = Empty/Homes)

ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group, fill = EmptPerc), 
colour = alpha("darkred", 1/2), size = 0.7) + scale_colour_gradient2() +
  ggtitle("Lambeth coloured by areas of highest % empty Homes")+
  theme(plot.title = element_text(hjust = 0.5))

Filter to RBKC
```{r}

AG2 <- AG %>% filter(LAD11NM == "Kensington and Chelsea")

#manually map ward codes to empty and missing homes

WardDat <- data.frame(Admin_ward_code = unique(AG2$Admin_ward_code), 
           Wardname = c("Abingdon","Brompton and Hans Town", "Courtfield", "Stanley", "Campden", "Colville", "Earl's Court", 
                      "Redcliffe", "Chelsea Riverside", "Kensal Green", "Golborne", "Royal Hospital", "Holland", "Notting Dale",
                      "Norland", "St. Helen's", "Pembridge", "Queen's Gate", "Dalgarno"),
           LowUse = c(744,1932,1060,593,664,330,572,587,371,0, 196, 829, 640,106,237, 149,331,846,87))

Chelsea <- EW2 %>% filter(LAD11NM == "Kensington and Chelsea") %>% 
  select(Admin_ward_code:WardPop) %>%
  distinct(Admin_ward_code, .keep_all=TRUE) %>% 
  left_join(., WardDat) %>% ungroup %>% mutate(PercEmpt = LowUse/WardHomes)

AG2 <-AG2 %>% left_join(., WardDat, by = "Admin_ward_code") %>% 
  filter(Wardname != "Kensal Green")%>% mutate(PercEmpt = LowUse/WardHomes)

ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group, fill = PercEmpt), 
colour = alpha("darkred", 1/2), size = 0.7) + scale_colour_gradient2() +
  ggtitle("Kensington and Chelsea low use property")+
  theme(plot.title = element_text(hjust = 0.5))

@@

prices <-read_csv("pp-2016.csv", col_names = FALSE )

#quick and dirty loses half the sales due to missing the postcode
test <- prices %>% mutate(X4 = gsub(" ", "", X4)) %>% left_join(., PstCdLSOA.raw %>% mutate(Postcode = gsub(" ", "", Postcode)), by = c("X4"="Postcode")) %>% filter(!is.na(lsoa11cd))

MeanWardPrice <- test %>% group_by(Admin_ward_code) %>% summarise( MeanPrice = mean(X2), counts =n() )

MeanWardPrice %>% ggplot(., aes(x= counts)) +geom_density()

@@

sum(WardDat2$vallow)/sum(WardDat2$LowUse)

Lest <- test %>% filter(X14 =="LEICESTERSHIRE")

Lest %>% filter(X2<15000000) %>% ggplot(., aes(x= X2)) + geom_density()

%>% group_by(X13) %>% summarise(mean = mean(X2))

Melt <- test %>% filter(X13 == "MELTON")

test %>% filter(grepl("chelsea", X13, ignore.case = TRUE)) %>%
  filter(X2<3000000) %>% ggplot(., aes(x= X2)) + geom_density()

@@

setwd("/home/jonno/Dropbox/SSE/Empty Homes/Regions-Complete/Region London")

Lambeth <- read_excel("LambethExemptionsLSOA.xlsx")[,1:4] %>% setNames(make.names(names(.))) %>% 
  mutate(type2 = ifelse(grepl("Empty", Exemption.type), "Empty", Exemption.type)) %>%
  group_by(type2, LSOA_CODE) %>% 
  summarise(Counts = n()) %>% 
  spread(., type2, Counts, fill = 0) %>% 
   left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% 
  group_by(Admin_ward_code) %>% mutate(Empty = sum(Empty), LowUse = Empty) %>% ungroup

@@

@@

Sutton <- read_excel("SuttonExemptionsLSOA.xlsx"  )[,1:6]

@@

@@

Plot Map
```{r}
AG2 <- bind_rows(CHELDAT,HAMDAT, WANDAT, LAMDAT, MERDAT, 
                 SOUDAT, KINDAT, TOWDAT, GREDAT) %>% 
  mutate(LowUsePerc = LowUse/WardHomes, 
         EmptyPerc = Empty/WardHomes,
         EmptyPercRank = percent_rank(Empty/WardHomes))

ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group, fill = EmptyPerc), 
colour = alpha("darkred", 1/2), size = 0.1) + scale_colour_gradient2() +
  labs(title = "All Boroughs Percentage Empty") +
  theme(plot.title = element_text(hjust = 0.5))

@@

@@

#single borough
GREDAT %>%
  mutate(LowUsePerc = LowUse/WardHomes, 
         EmptyPerc = Empty/WardHomes,
         EmptyPercRank = percent_rank(Empty/WardHomes)) %>%
ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill = EmptyPerc), 
colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2()

@@

test <- read_excel("Barrow-in-FurnessExemptionsLSOA.xlsx", sheet=1) %>% setNames(make.names(names(.))) %>% .[,1:4] %>% filter(Current.Discount.Type.Code !="SINGLE") %>% group_by(LSOA_CODE) %>%
  summarise(Empty = n())

Barrow2 <- test %>% left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% mutate(EmptyPerc = Empty/Homes)

test2 <- test %>% left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd")) %>% mutate(EmptyPerc = Empty/Homes)

ggplot()+ geom_polygon(data=test2, aes(long, lat, group = group, fill = EmptyPerc), 
colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() + ggtitle("Barrow in Furness Emptyness %")
```

```{r}
test <- read_excel("South LakelandExemptionsLSOA.XLSX", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
  spread(key= Exemption.type, value = counts, fill = 0) %>% mutate(Empty = rowSums(.[,2:9])) %>%
  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% mutate(EmptyPerc = Empty/Homes)

test2 <- test %>% left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd"))

@@

Cornwall %>% left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd"))  %>% 
  ggplot(.)+ 
  geom_polygon( aes(long, lat, group = group, fill = LowUsePerc), 
colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() + ggtitle("Cornwall Empty and second Homes %")+
  theme(plot.title = element_text(hjust = 0.5))

 Cornwall %>% filter(Admin_ward_code !="E05009195") %>% summarise(x =cor(MeanPrice, WardLowUsePerc, use = 'complete.obs'))

 Cornwall %>% ggplot(., aes(y=MeanPrice, x= WardLowUsePerc )) + geom_point() +
   labs(title = "Relationshibetween LowUse Percentage and Mean Price in Ward")+
  theme(plot.title = element_text(hjust = 0.5))

@@

>>>>

PCLB0 is second homes, PCLC0 is long term empty, PCLC100 is empty and unfurnished up to six months and PCLD100 is undergoing major repairs up to 12 months.

@@

Mean household income 31920
https://www.ons.gov.uk/peoplepopulationandcommunity/personalandhouseholdfinances/incomeandwealth/datasets/nowcastinghouseholdincomeintheuk

@@

setwd(file.path(RegionsComp, "Region East of England"))
list.files()

test <- read.xlsx("FOI IMT178324 SuffolkCoastal.xlsx")

unique(test$Exemption.type)

```{r}
# setwd(ShapeFiles)
# 
# wards.shp <- readShapeSpatial("London_Ward.shp")
# coords <- coordinates(wards.shp)
# WardsAdj <- poly2nb(wards.shp, queen= FALSE)
# plot(wards.shp, border="grey")
# plot(WardsAdj, coords, add=TRUE, col="red")
# 
# test <- (nb2mat(WardsAdj)>0)*1
# 
# 
# g=graph.data.frame(WardsAdj)
# get.adjacency(WardsAdj,sparse=FALSE)

@@

if(file.exists(file.path(DataFolder,"shapeframe.rds"))){
 AG<- readRDS(file.path(DataFolder,"shapeframe.rds"))
} else{
    setwd(LSOAshapedata)

@@

@@

prices <-read_csv("pp-2016.csv", col_names = FALSE ) %>% 
  mutate(X4 = gsub(" ", "", X4)) %>% 
  left_join(., PstCdLSOA.raw %>% mutate(Postcode = gsub(" ", "", Postcode)), 
            by = c("X4"="Postcode")) %>% 
  filter(!is.na(lsoa11cd)) %>% mutate(Prime = X2>1e6, SuperPrime = X2>1e7)

MeanWardPrice <- prices %>% 
  group_by(Admin_ward_code) %>% 
  summarise( MeanPrice = mean(X2), 
             MedianPrice = median(X2),counts =n(),  
             Prime = sum(Prime), 
             SuperPrime = sum(SuperPrime)) %>% 
  mutate(TotPrime = Prime/sum(Prime), TotSupPrime = SuperPrime/sum(SuperPrime),
         PrimePerc = Prime/counts, SuperPrimePerc = SuperPrime/counts)

MeanWardPrice %>% ggplot(., aes(x= counts)) + geom_density()

@@

setwd(DataFolder)
list.files()

#Unnfordability at EW level salery 2014-2015
mean(prices$X2)/31920

#is mean income estimates
IncomeEst <- read_excel("1smallareaincomeestimatesdataupdate.xls", sheet = 4, skip = 4) %>%
  setNames(make.names(names(.)) %>% 
             gsub("\\.(?=\\.*$)", "", ., perl=TRUE)) #removes trailing full stop.

test2 <- prices %>% left_join(., select(EW2, ECODE, MSOA11CD), 
                              by =c("lsoa11cd"="ECODE")) %>%
  group_by(MSOA11CD) %>%
  summarise(MeanPrice = mean(X2), counts = n()) %>%
  left_join(., IncomeEst, by=c("MSOA11CD"= "MSOA.code")) %>%
  mutate(Yearly.income= 52 * Total.weekly.income, ratio = MeanPrice/Yearly.income)

test2 %>% ggplot(.,aes(x=ratio)) +geom_density()

sum(test2$ratio>6)/nrow(test2)  #about 50% EW
test2 %>% filter(Region.name == "London") %>% mutate(HighRatio = ratio>10) %>%
  summarise(total = sum(HighRatio)/n())

@@

setwd(file.path(RegionsComp, "Region London"))

Lambeth <- read_excel("LambethExemptionsLSOA.xlsx")[,1:4] %>%
  setNames(make.names(names(.))) %>%
  group_by(Exemption.type, LSOA_CODE) %>% 
  summarise(Counts = n()) %>% 
  spread(., Exemption.type, Counts, fill = 0) %>%
    setNames(make.names(names(.))) %>%
  mutate(LowUse = rowSums(.[,c(2:5, 24:25)]), Empty = LowUse - Empty.Class.A-Empty.Class.B) %>%
   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))

@@

#Camden

test <- read.xlsx("Camden Exemptions LSOA - 20891480.xlsx")[1:4]

Camden <- read.xlsx("Camden Discounts LSOA - 20891480.xlsx" )[,1:4] %>%
  group_by(Discount.type, LSOA_CODE) %>% 
  summarise(Counts = n()) %>% 
  spread(., Discount.type, Counts, fill = 0) %>% 
  mutate(LowUse = rowSums(.[,-1]), Empty = LowUse - B) %>%
   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))

CAMDAT <- AG %>% filter(LAD11NM == "Camden") %>% 
  left_join(., select(Camden, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))

#Bromley

Bromley <- read.xlsx("Copy of BromleyExemptionsLSOA.xlsx")[,1:4] %>%
  setNames(make.names(names(.))) %>%
  group_by(Exemption.type, LSOA_CODE) %>% 
  summarise(Counts = n()) %>% 
  spread(., Exemption.type, Counts, fill = 0) %>%
    setNames(make.names(names(.))) %>%
  mutate(LowUse = rowSums(.[,c(6:8,29:31)]), Empty=LowUse - Empty.Class.B) %>%
   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))

BRODAT <- AG %>% filter(LAD11NM == "Bromley") %>% 
  left_join(., select(Bromley, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))

#Haringey

Haringey <- read.xlsx("Haringey_Exemptions_Discounts_LSOA.xlsx")[c(1,3,5)] %>%
    setNames(make.names(names(.))) %>%
  group_by(Exemption...Discount.type, LSOA_CODE) %>% 
  summarise(Counts = n()) %>%
  spread(., key = Exemption...Discount.type, 
         value = Counts, fill = 0) %>%
    setNames(make.names(names(.))) %>%
  mutate(LowUse = rowSums(.[,21:25]), Empty=LowUse - PCLB0) %>%
   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))

HARDAT <- AG %>% filter(LAD11NM == "Haringey") %>% 
  left_join(., select(Haringey, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))

@@

Sutton <- read_excel("SuttonExemptionsLSOADiscount.xlsx"  )[,1:6] %>%
    setNames(make.names(names(.))) %>%
  group_by(Exemption.type, LSOA_CODE) %>% 
  summarise(Counts = n()) %>%
  spread(., key = Exemption.type, 
         value = Counts, fill = 0) %>%
    setNames(make.names(names(.)))%>%
  mutate(LowUse = rowSums(.[,-1]), Empty=LowUse - PCLB0) %>%
   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))

SUTDAT <- AG %>% filter(LAD11NM == "Sutton") %>% 
  left_join(., select(Sutton, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))

#Richmond

Richmond <- read_csv("Richmond_2.csv" )[1:4] %>% setNames(make.names(names(.))) %>%
  rename(Exemption.type = Discount.type) %>%
  mutate(Exemption.type = Exemption.type %>% trimws %>%
           make.names %>% 
           gsub("\\.{2,}" , ".", .)) %>%
  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
  spread(key= Exemption.type, value = counts, fill = 0) %>% 
    setNames(make.names(trimws(names(.)))) %>%
    mutate(LowUse = rowSums(.[,-1]), Empty = LowUse) %>%
  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)

RICDAT <- AG %>% filter(LAD11NM == "Richmond upon Thames") %>% 
  left_join(., select(Richmond, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))

#Hillingdon

Hillingdon <- read.xlsx("HillingdonDiscountsLSOA.XLSX" )[1:4] %>% mutate(Exemption.type = Exemption.type %>% trimws %>%
           make.names %>% 
           gsub("\\.{2,}" , ".", .)) %>%
  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
  spread(key= Exemption.type, value = counts, fill = 0) %>% 
    setNames(make.names(trimws(names(.)))) %>%  
  mutate(LowUse = rowSums(.[,-1]), Empty = LowUse- Class.B.Second.Home) %>%
  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)

HILDAT <- AG %>% filter(LAD11NM == "Hillingdon") %>% 
  left_join(., select(Hillingdon, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))

#Bexley

Bexley <- read.xlsx( "Bexley Exemptions.xlsx" , colNames = FALSE) %>%
  setNames(c("Exemption.type", "LSOA_CODE", "X3", "X4")) %>%
  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
  spread(key= Exemption.type, value = counts, fill = 0) %>% 
    setNames(make.names(trimws(names(.)))) %>% 
  mutate(LowUse = rowSums(.[,c(2,19,20)]), Empty = LowUse) %>%
  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)

BEXDAT <- AG %>% filter(LAD11NM == "Bexley") %>% 
  left_join(., select(Bexley, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))

@@

Chel2 <- Chelsea %>% left_join(., MeanWardPrice) %>% left_join(., EW2) %>%
  mutate(LowUsePerc = LowUse/WardHomes)

cor(Chel2$PrimePerc, Chel2$LowUsePerc)
cor(Chel2$MeanPrice, Chel2$LowUsePerc)

Chel2 %>%
  mutate(PrimePerc = PrimePerc*100, LowUsePerc = LowUsePerc*100) %>% 
  ggplot(.,aes(x= PrimePerc, LowUsePerc)) +geom_point() + 
  geom_smooth(method ="lm", se = FALSE) +
  labs(title = "Relationship between % of Prime Sales and % Low Use", 
       x = "% of properties sold in 2016 over £1M by electoral ward",
       y = "% of properties either empty or second homes") +
  theme(plot.title = element_text(hjust = 0.5))  +
  coord_cartesian(xlim = c(15,78), expand = TRUE)

@@

Plot Map
```{r}
AG2 <- bind_rows(CHELDAT,HAMDAT, WANDAT, LAMDAT, MERDAT, 
                 SOUDAT, KINDAT, TOWDAT, GREDAT, CAMDAT, 
                 BRODAT, HARDAT, RICDAT, HILDAT, BEXDAT,
                 SUTDAT) %>% 
  mutate(LowUsePerc = LowUse/WardHomes, 
         EmptyPerc = Empty/WardHomes,
         EmptyPercRank = percent_rank(Empty/WardHomes))

ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group, fill = EmptyPerc), 
colour = alpha("darkred", 1/2), size = 0.1) + scale_colour_gradient2() +
  labs(title = "9 Boroughs: Ward Level % Empty") +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())

@@

AG2 %>% 
  ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill =EmptyPercRank), 
colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2()

@@

#single borough
CHELDAT %>%
  mutate(LowUsePerc = LowUse/WardHomes*100, 
         EmptyPerc = Empty/WardHomes,
         EmptyPercRank = percent_rank(Empty/WardHomes)) %>%
ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill = LowUsePerc), 
colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() +
  labs(title = "Kensington and Chealsea: Ward Level % Low Use") +
  theme(plot.title = element_text(hjust = 0.5))+ 
  scale_fill_continuous(name = "Percentage")

#SIngle borough detail
SUTDAT %>%
  mutate(LowUsePerc = LowUse/Homes, 
         EmptyPerc = Empty/Homes,
         EmptyPercRank = percent_rank(Empty/Homes)) %>%
ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill = LowUsePerc), 
colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() +
  ggtitle("Kensington and Chelsea ward level % low use") + 
  theme(plot.title = element_text(hjust = 0.5))
```

@@

Barrow <- read_excel("Barrow-in-FurnessExemptionsLSOA.xlsx", sheet=1) %>% setNames(make.names(names(.))) %>% .[,1:4] %>% filter(Current.Discount.Type.Code !="SINGLE") %>% group_by(LSOA_CODE, Current.Discount.Type.Code) %>%
  summarise(Empty = n()) %>% 
  spread(key=Current.Discount.Type.Code, value = Empty, fill = 0 ) %>% ungroup %>%
 mutate( LowUse = rowSums(.[-1]), Empty = LowUse-PCLB0)

Barrow2 <- Barrow %>% 
  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% 
  mutate(LowUsePerc = LowUse/Homes, EmptyPerc = Empty/Homes)

Barrow3 <- Barrow %>% left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd")) %>% 
  mutate(LowUsePerc = LowUse/Homes, EmptyPerc = Empty/Homes)

ggplot()+ geom_polygon(data=Barrow2, aes(long, lat, group = group, fill = PCLB0), 
colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() + ggtitle("Barrow in Furness Emptyness %")
```

```{r}
SLakeland <- read_excel("South LakelandExemptionsLSOA.XLSX", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
  spread(key= Exemption.type, value = counts, fill = 0) %>% 
  mutate(Empty = rowSums(.[,2:9])) %>%
  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% mutate(EmptyPerc = Empty/Homes)

SLakeland2 <- SLakeland %>% left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd"))

ggplot()+ geom_polygon(data=SLakeland2, aes(long, lat, group = group, fill = EmptyPerc), 
colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() + ggtitle("Barrow in Furness Emptyness %")

bind_rows(Barrow3,SLakeland2) %>%ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill = EmptyPerc), 
colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() + 
  ggtitle("Cumbria Empty Percentage")+
  theme(axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())

@@

Cornwall %>% mutate(LowUsePerc = LowUsePerc*100) %>% 
  left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd"))  %>% 
  ggplot(.)+ 
  geom_polygon( aes(long, lat, group = group, fill = LowUsePerc), 
colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() + ggtitle("Cornwall: Ward level Empty and Second Homes %")+
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_fill_continuous(name = "Percentage")

CornCor <- Cornwall %>% 
  #filter(Admin_ward_code !="E05009195") %>% 
  summarise(x =cor(MedianPrice, WardLowUsePerc, use = 'complete.obs'))

 Cornwall %>% ggplot(., aes(y=MedianPrice, x= WardLowUsePerc )) + geom_point() +
   labs(title = "Mean Price vs Low Use % by ward in Cornwall",
        x = "Low Use Percentage by Ward", 
        y = "Mean Price") +
  theme(plot.title = element_text(hjust = 0.5)) + 
    annotate("text", 
             label = paste0("Correlation =", signif(CornCor[1,1],2)), 
             x = 0.35 , y = 7.5e5, size = 5) +
   geom_smooth(method = "lm", se = FALSE)

 #"Cornwall: Relationship between LowUse\n Percentage and Mean Price in Ward"

@@

#Suffolk

setwd(file.path(RegionsComp, "Region East of England"))
list.files()

CoastWave <- bind_rows(read.xlsx("FOI IMT178324 SuffolkCoastal.xlsx")[1:4] , read.xlsx("FOI IMT178324 Waveney.xlsx")[1:4]) %>% setNames(make.names(names(.))) %>%
  mutate(Exemption.type = Exemption.type %>% trimws %>%
           make.names %>% 
           gsub("\\.{2,}" , ".", .)) %>%
  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
  spread(key= Exemption.type, value = counts, fill = 0) %>% 
    setNames(make.names(trimws(names(.)))) %>%
    mutate(LowUse = rowSums(.[,c(5,6,13,14,16:18)]), Empty = LowUse -Second.Home.Class.A -Second.Home.Class.B) %>%
  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)

CoastWave %>% left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd"))  %>% 
  ggplot(.)+ 
  geom_polygon( aes(long, lat, group = group, fill = LowUsePerc), 
colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2()

#corellation
CoastWave %>% 
  #filter(Admin_ward_code !="E05009195") %>% 
  summarise(x =cor(MeanPrice, WardLowUsePerc, use = 'complete.obs'))

 CoastWave %>% ggplot(., aes(y=MeanPrice, x= WardLowUsePerc )) + geom_point() +
   labs(title = "Coastal and Waveny: Relationship between LowUse\n Percentage and Mean Price in Ward")+
  theme(plot.title = element_text(hjust = 0.5))
